ES Models: Random Forest

### 2025-03-17 randomforest_kl.Qmd
random forest kl

    p1 <- plotPartial(sed_export_base.ann_agr_pland.pdp, main = "Sediment base")
    p2 <- plotPartial(sed_export_margin.ann_agr_pland.pdp, main = "Sediment margin")
    p3 <- plotPartial(sed_export_base.ntr_pland.pdp, main = "Sediment base")
    p4 <- plotPartial(sed_export_margin.ntr_pland.pdp, main = "Sediment margin")
    grid.arrange(p1, p3, p2, p4, ncol = 2)

>>>>

    p1 <- plotPartial(sed_export_base.ann_agr_pland.pdp, main = "Sediment base", rug = TRUE)
    p2 <- plotPartial(sed_export_margin.ann_agr_pland.pdp, main = "Sediment margin")
    p3 <- plotPartial(sed_export_base.ntr_pland.pdp, main = "Sediment base")
    p4 <- plotPartial(sed_export_margin.ntr_pland.pdp, main = "Sediment margin")
    grid.arrange(p1, p3, p2, p4, ncol = 2)
